% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2010 Jason R. Blevins
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}

% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
%\usepackage[osf]{xagaramon}

% Set your name here
\def\name{Kristen M. Thyng}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {tidal energy,cfd,gfd,roms,university of washington},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.75in, 9.0in},
  left=0.85in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}
\input{../../LatexFiles/macros}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  \href{http://www.tamu.edu/}{Texas A\&M University} \\
  \href{http://ocean.tamu.edu/}{Department of Oceanography} \\
  3146 TAMU \\
  College Station, TX 77843-3146 \\
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  (979) 845-1231 \\
  \href{mailto:kthyng@tamu.edu}{\tt kthyng@tamu.edu} \\
  \href{http://kristenthyng.com}{\tt http://kristenthyng.com} \\
\end{minipage}

\section*{Education}

\begin{itemize}

  \item Ph.D. Mechanical Engineering, University of Washington, June 2012.

    \begin{itemize}
	\item   ``Numerical Simulation of Admiralty Inlet, WA, with Tidal Hydrokinetic Turbine Siting Application''
    \item \textit{Committee:}
      \href{http://faculty.washington.edu/rileyj/}{James J. Riley} (chair),
      \href{http://www.me.washington.edu/research/faculty/aaliseda/}{Alberto Aliseda},
      \href{http://faculty.washington.edu/kawase/}{Mitsuhiro Kawase},
      \href{http://www.me.washington.edu/research/faculty/bpolagye/}{Brian Polagye}, and
      \href{http://www.atmos.washington.edu/~durrand/}{Dale Durran}.

    % EXTENDED
    \item \textit{Included work on tidally-generated headland vorticity, turbulence modeling using the $k$-$\varepsilon$ model, and tidal current turbine siting.}

    \end{itemize}

  \item M.Sc. Applied Mathematics, University of Washington, 2007.

  \item B.A. Physics, Whitman College, 2005.

    \begin{itemize}

    \item \textit{Minor:} Mathematics, \textit{Honors:} \href{https://www.whitman.edu/content/catalog/financial-aid}{Walter Brattain Scholarship}, \textit{Study Abroad:}
      \href{http://www.semesteratsea.org/}{Semester at Sea},
      Fall 2001.

    \end{itemize}

\end{itemize}

\section*{Employment}
%\section*{Research Experience}

\subsection*{Texas A\&M University, Department of Oceanography}

\begin{itemize}

\item Postdoctoral Research Associate, \href{http://pong.tamu.edu/~rob/}{Robert D. Hetland}, 2012--Present.

% EXTENDED
\item \textit{Used particle tracking to investigate the origin of harmful algal bloom initiation on the Texas-Louisiana shelf and to understand the connectivity of Galveston Bay to the shelf for application to oil spill response. Particle tracking was applied to existing ROMS model output.}

\end{itemize}

\subsection*{University of Washington, Department of Mechanical Engineering}

\begin{itemize}

\item Research Assistant,
  \href{http://faculty.washington.edu/rileyj/}{James J. Riley},
 2007--2012.

 % EXTENDED
\item \textit{Set up and ran a numerical simulation of the Puget Sound using unstructured mesh ocean model SUNTANS, then set up a numerical simulation of the Puget Sound entrance channel, Admiralty Inlet, in the structured mesh ocean model ROMS. These models were used to address research questions related to the potential siting of tidal current turbines in the Puget Sound.}

\end{itemize}

\subsection*{Prometheus Energy Co.}

\begin{itemize}

\item Jr. Scientist,
  \href{http://www.prometheus-energy.com/aboutus/team.php}{John A. Barclay},
  Summer 2006.

% EXTENDED
\item \textit{Updated and improved a code modeling the cooling of an active magnetic regenerative refrigerator as research for a liquid natural gas energy company.}

\end{itemize}

\subsection*{Whitman College,
  Physics Department}

\begin{itemize}

\item Fairbank Physics Research Assistant,
  \href{http://people.whitman.edu/~hoffman/}{Kurt Hoffman},
  Summer 2004.

% EXTENDED
\item \textit{Evaluated existing second year physics labs and researched and initiated some new ones.}

\item First-Year Physics Lab Assistant,  Fall 2003--Spring 2004.

% EXTENDED
\item \textit{Set up and took down the first year physics lab each week}

\item First-Year Physics Lab Reorganization, 
 \href{http://people.whitman.edu/~beckmk/}{Mark Beck},
 Summer 2003.

 % EXTENDED
 \item \textit{Edited, reworked, and reorganized the first year physics lab}

\end{itemize}

\section*{Research}

\subsection*{Publications}

\subsubsection*{Peer-reviewed}

\begin{itemize}

% \item Thyng, K. M., J. J. Riley, M. Kawase, ``Vorticity Dynamics in an Energetic Estuary Using a Simulation in ROMS'' (in preparation).

\item Thyng, K. M., R. D. Hetland, M. T. Ogle, X. Zhang, F. Chen, L. Campbell, ``Origins of harmful algal blooms along the Texas coast'' (submitted).

\item Thyng, K. M. and T. Roc, ``Tidal current turbine power capture and impact in an idealised channel simulation,'' European Wave and Tidal Energy Conference, Aalborg, Denmark, 2013 (submitted).

\item Thyng, K. M., J. J. Riley, J. Thomson, ``Turbulence in a tidal channel: $k$-$\varepsilon$ model and data'' (submitted).

\item Thyng, K. M., J. J. Riley, J. Thomson, ``Inference of Turbulence Parameters from a ROMS Simulation using the $k$-$\varepsilon$ Closure Scheme,'' 2012 (submitted).

\item Thyng, K. M., ``Numerical Simulation of Admiralty Inlet, WA, with Tidal Hydrokinetic Turbine Siting Application.'' Ph.D. Dissertation, June 2012.

\item Roc, T., K. M. Thyng and D. Conley, ``Applying a numerical decision-making tool for tidal current turbine (TCT) planning projects to the Puget Sound estuary - Early Results'', Proc. EWTEC, 2011.

\item Kawase, M., and K. M. Thyng. ``Three-dimensional Hydrodynamic Modelling of Inland Marine Waters of Washington State, United States, for Tidal Resource and Environmental Impact Assessment.'' IET Renewable Power Generation. 4.6 (2010): 568-578. 

\end{itemize}

\subsubsection*{Other}

\begin{itemize}

\item Thyng, K. M. and J. J. Riley (2010). \href{http://froude.me.washington.edu/papers/thyng2010.pdf}{``Idealized Headland Simulation for Tidal Hydrokinetic Turbine Siting Metrics''}. \textit{OCEANS 2010 MTS/IEEE Conference,} Seattle, WA, USA.

\end{itemize}

\subsection*{Conference and Seminar Presentations}

\begin{itemize}

\item Invited panelist on best practices in data visualization, SciPy Conference, Austin, TX, June 27, 2013.

\item K. M. Thyng, J. J. Riley, and M. Kawase, ``Vorticity Dynamics in Admiralty Inlet, Puget Sound,'' invited speaker at the Gordon Research Seminar: Coastal Ocean Circulation, University of New England, June 9, 2013.

\item K. M. Thyng, R. D. Hetland, X. Zhang, L, Campbell, ``Origins of Harmful Algal Blooms Along the Texas Coast,'' ASLO Aquatic Sciences Meeting, New Orleans, LA, February 21, 2013.

\item K. M. Thyng and J. J. Riley, ``Turbulence Modeling in a Numerical Model for Tidal Hydrokinetic Energy Siting,'' invited speaker at Texas A\&M University, October 13, 2011.

\item T. Roc, K. M. Thyng, D. Conley, ``Applying a numerical decision-making tool for tidal current turbine (TCT) planning projects to the Puget Sound estuary - Early Results,'' 8th European Wave and Tidal Energy Conference, Southampton, 2011.

\item K. M. Thyng and J. J. Riley, \href{http://froude.me.washington.edu/presentations/nnmrec050511.pdf}{``Site Modeling for Tidal Turbines''}, 2nd Annual OSU-UW Northwest National Marine Renewable Energy Center Conference, University of Washington, May 5, 2011.

\item K. M. Thyng and J. J. Riley, ``Understanding New Admiralty Inlet Simulation'', \href{http://faculty.washington.edu/pmacc/mug/mug_home.html}{MoSSea Users Group}, School of Oceanography, University of Washington, May 4, 2011.

\item K. M. Thyng and J. J. Riley, \href{http://faculty.washington.edu/pmacc/mug/meetings/Thyng_MUG_talk.pdf}{``Modeling for Tidal Energy Analysis''}, \href{http://faculty.washington.edu/pmacc/mug/mug_home.html}{MoSSea Users Group}, School of Oceanography, University of Washington, January 19, 2011.

\item K. M. Thyng and J. J. Riley, \href{http://froude.me.washington.edu/presentations/mess101110/mess101110.pdf}{``Tidal Energy and Turbine Siting Metrics''}, Mechanical Engineering Student Seminar, University of Washington, October 11, 2010.

\item K. M. Thyng and J. J. Riley, \href{http://froude.me.washington.edu/presentations/oceans2010/oceans2010.pdf}{``Idealized Headland Simulation for Tidal Hydrokinetic Turbine Siting Metrics''}, OCEANS 2010 MTS/IEEE Seattle, September 21, 2010.

\item K. M. Thyng and J. J. Riley, \href{http://froude.me.washington.edu/presentations/inore2010/inore2010.pdf}{``Working Toward Numerical Simulations of Admiralty Inlet for Tidal Hydrokinetic Energy,''} \href{http://inore.org/}{4th Annual INORE Symposium, Dartmouth, UK, May 12, 2010}.

\item K. M. Thyng and J. J. Riley, \href{http://froude.me.washington.edu/presentations/SIAM-4-21-09.pdf}{``Tidal Energy in the Puget Sound''}, SIAM UW, April 21, 2009.

\item K. M. Thyng and J. J. Riley, \href{http://froude.me.washington.edu/presentations/SIAM-5-29-08.pdf}{``Tidal Energy in the Puget Sound''}, SIAM UW, May 29, 2008.

%  \begin{itemize}
%
%  \item \href{http://econ.duke.edu/~brossi/ERIDIdentifProgram.htm}{ERID Conference on Identification Issues in Economics},
%    Duke University, October 3, 2008.
%
%  \end{itemize}

\end{itemize}

\subsection*{Poster Presentations}

\begin{itemize}

\item K. M. Thyng, J. J. Riley, and M. Kawase, ``Vorticity Dynamics in Admiralty Inlet, Puget Sound,'' Gordon Research Conference: Coastal Ocean Circulation, University of New England, June 9--14, 2013.

\item \href{http://pong.tamu.edu/~kthyng/posters/pecs.pdf}{ROMS Turbulence Parameter Comparisons with Field Data}, The Physics of Estuaries and Coastal Seas (PECS) Symposium, 12--16 August 2012, New York City.

\item Nested ROMS Model of a Complex Estuarine Channel, Puget Sound, WA. Gordon Research Conference: Coastal Ocean Modeling,
  Mt. Holyoke College, South Hadley,  MA, 
  June 26--July 1, 2011.
  
\item \href{http://froude.me.washington.edu/presentations/GPSS051311.pdf}{Site Modeling for Tidal Turbines}. Graduate and Professional Student Senate Science and Policy Summit, University of Washington, May 13, 2011.

\item \href{http://froude.me.washington.edu/presentations/InorePoster2010/inore.pdf}{Numerical Modeling for Tidal
Hydrokinetic Turbine Siting}. \href{http://www.inore.org}{4th Annual INORE Symposium, Dartmouth, UK, May 9, 2010}.

\item \href{http://froude.me.washington.edu/presentations/inore_poster2009.pdf}{Estuary Modeling for Tidal Energy in Puget Sound, WA}. \href{http://www.inore.org}{3rd Annual INORE Symposium, Gent, Belgium, May 26, 2009}.

\end{itemize}

\subsection*{Professional Activities}

\begin{itemize}

\item Member, \href{http://www.siam.org/}{Society for Industrial and Applied Mathematics},
  2008--Present.

\item Member, \href{http://www.agu.org/}{American Geophysical Union},
  2010--Present.

\item Member, \href{http://www.ieee.org/}{Institute of Electrical and Electronics Engineers},
  2010--Present.

\item Member, \href{http://www.aslo.org/}{Association for the Sciences of Limnology and Oceanography},
  2012--Present.

%\item Referee for:
%
%  \begin{itemize}
%  \item \textit{Economic Inquiry} % 2008 (1)
%  \item \textit{Journal of Business and Economic Statistics} % 2009 (1)
%  \item \textit{Journal of Econometrics} % 2009 (1)
%  \item \textit{Scandinavian Journal of Statistics} % 2009 (1)
%  \end{itemize}

\end{itemize}

\subsection*{Conferences and Workshops Attended}

\begin{itemize}

\item Gordon Research Seminar and Gordon Research Conference: Coastal Ocean Circulation, University of New England, June 9--14, 2013.

\item Association for the Sciences of Limnology and Oceanography (ASLO) 2013 Aquatic Sciences Meeting, February 17--22, 2013, New Orleans, Louisiana.

\item Gulf Of Mexico: Oil Spill \& Ecosystem Science Conference, January 21--23, 2013, New Orleans, Louisiana.

\item Subsea Blowout Modeling Workshop, University of California, Berkeley, November 27--28, 2012.

\item The Physics of Estuaries and Coastal Seas (PECS) Symposium, 12-16 August 2012, New York City.

\item \href{http://www.grc.org/programs.aspx?year=2011&program=coastal}{Gordon Research Conference: Coastal Ocean Modeling},
  Mt. Holyoke College, South Hadley,  MA, 
  June 26--July 1, 2011.

\item \href{http://www.oceans10mtsieeeseattle.org/}{OCEANS 2010 MTS/IEEE},
  Seattle,
  September 20--23, 2010.

\item \href{http://www.inore.org}{4th Annual International Network of Offshore Renewable Energy researchers (INORE) Symposium},
  Dartmouth, UK,
  May 9--14, 2010.

\item \href{http://www.agu.org/meetings/os10/}{2010 Ocean Sciences Meeting},
  Oregon Convention Center,
  February 22--26, 2010.

\item \href{http://www.oce.uri.edu/ecm11/index.html}{Eleventh International Conference on Estuarine and Coastal Modeling},
  Seattle, WA,
  November 4--6, 2009.

\item \href{http://www.inore.org}{3rd Annual International Network of Offshore Renewable Energy researchers (INORE) Symposium},
  Gent, Belgium,
  May 24--28, 2009.

\item \href{http://www.ukerc.ac.uk/support/tiki-index.php?page=0608UKERCSummerSchool}{U.K. Energy Research Council (UKERC) Energy Summer School 2008},
  Roehampton, London, UK,
  June 23--27, 2008.

\end{itemize}

\section*{Teaching Experience}

\subsection*{Texas A\&M University, Department of Oceanography}

\begin{itemize}

\item Guest Lecturer, Oceanography 410: Introduction to Physical Oceanography, 2013

\end{itemize}

\subsection*{University of Washington, Department of Mechanical Engineering}

\begin{itemize}

\item Teaching Assistant,
  \href{http://www.washington.edu/students/crscat/meche.html#me323}{Thermodynamics, ME 323},
  \href{http://www.me.washington.edu/research/faculty/malte/}{Phil Malte},
  Fall 2007.

\end{itemize}

\subsection*{Tutoring}

\begin{itemize}
	\item Trigonometry and physics, November - December 2007.
	\item Algebra, geometry and trigonometry, January - March 2007.
	\item AP Calculus BC exam, March - May 2007.
	\item Calculus, June - July  2007.
\end{itemize}

\section*{Honors \& Awards}

\begin{itemize}

\item SciPy John Hunter Excellence in Plotting Competition 2013: 2nd place.

\item Outstanding Female Award, Mechanical Engineering. Society of Women Engineers, University of Washington. January 25, 2012.

\item \href{http://inore.org/news/icis_travel_grants/}{International Collaboration Incentive Scheme grant}, a collaborative research grant through INORE, 2011.

\item \href{http://www.inore.org}{Best Symposium Poster}, INORE Symposium, 2010.

\item \href{https://www.whitman.edu/content/catalog/financial-aid}{Walter Brattain Scholarship}, 2001-2005.

%\item Holy Mother Marie Rose Scholarship, 1997-2001.
%
%\item Valedictorian, 2001

\end{itemize}

\section*{Service}
\begin{itemize}
  \item Organizer and fund raiser for Women in Scientific Computing event, June 27, 2013.
  \item Referee, Ocean Dynamics
  \item Referee, International Conference on Ocean, Offshore and Arctic Engineering (OMAE) 2013
	\item Referee, National Oceanic and Atmospheric Administration
	\item Referee, European Wave and Tidal Energy Conference
	\item \href{http://www.amath.washington.edu/~siamuw/math-fair.html}{Math and Science Fair}, Lockwood Elementary School, March 15, 2011.
	\item \href{http://www.amath.washington.edu/~siamuw/math-fair.html}{Math and Science Fair}, Lockwood Elementary School, December 15, 2010.
	\item Math and Science Fair, Emerson Elementary School, June 8, 2010.
	\item An Introduction to Tidal Energy Research in the Puget Sound. UW Robinson School Summer Challenge, July 19, 2010.
	\item Volunteer at \href{http://www.globalmarinerenewable.com/}{3rd Annual Global Marine Renewable Energy Conference},  Bell Harbor International Convention Center,  April 14--15, 2010.
\end{itemize}

\section*{Skills}
\begin{itemize}
	\item Extensively utilized SUNTANS and ROMS ocean modeling codes.
	\item Proficiency in Python, FORTRAN, C, MatLab, and \LaTeX.
	\item Linux system administration.
	\item Experience using a cluster and parallel computing.
	\item Experience with HTML.
\end{itemize}

% \section*{Other Interests}
% \begin{itemize}
% 	\item Hiking
% 	\item Mountaineering
% 	\item Road and trail running
% \end{itemize}

% \bigskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}
